Structural controllability of ecological networks

### 2018-06-19 paper/supp-info.Rmd
Typo in chunk name
JOE uses Supporting Information

---
title: "Structural controllability of ecological networks"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r tab-controllabillity-model-results, results = "asis", sanitize = FALSE}
drake::loadd(controllability_models)

>>>>

---
title: "Structural controllability of ecological networks"
subtitle: "Supporting Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r tab-controllability-model-results, results = "asis", sanitize = FALSE}
drake::loadd(controllability_models)
